Brain region specific differential expression analysis (all 7 regions/one region at a time)

### 2017-05-16 code/Rmd/regionLevelDiffExpAnlz.Rmd
Minor modifications

  # Formulate covariates matrix
  FactorCov = c('Diagnosis', 'Batch', 'Gender')
  ContCov = c('RIN', 'AAD', 'PMI',  'PCT_PF_READS_ALIGNED', 'PCT_CODING_BASES', 
              'PCT_INTERGENIC_BASES', 'PCT_INTRONIC_BASES', 'PCT_RIBOSOMAL_BASES')
  cov[,FactorCov] = lapply(cov[,FactorCov], as.factor)
  cov[,ContCov] = lapply(cov[,ContCov], as.numeric)
  rownames(cov) = cov$SampleID
  cov = cov[,c(FactorCov, ContCov)]
  # assocStat = getAssociationStatistics(cov)

  # Perform differential expression between case-control
  varOfInterest = c('Diagnosis', 'Batch', 'Gender', 'RIN', 'AAD', 'PMI', 
                    'PCT_PF_READS_ALIGNED', 'PCT_INTERGENIC_BASES', 'PCT_INTRONIC_BASES', 
                    'PCT_RIBOSOMAL_BASES')
  contVar = 'Diagnosis'

@@

  # Perform differential expression between case-control in a gender specific manner
  cov$Diagnosis.Gender = factor(paste(cov$Diagnosis, cov$Gender, sep = '.'))
  varOfInterest = c('Diagnosis.Gender', 'Batch', 'RIN', 'AAD', 'PMI', 
                    'PCT_PF_READS_ALIGNED', 'PCT_INTERGENIC_BASES', 'PCT_INTRONIC_BASES', 
                    'PCT_RIBOSOMAL_BASES')
  contVar = 'Diagnosis.Gender'

@@

  # Perform differential expression between case-control in a AAD specific manner
  varOfInterest = c('Diagnosis', 'Gender', 'Batch', 'RIN', 'AAD', 'PMI', 
                    'PCT_PF_READS_ALIGNED', 'PCT_INTERGENIC_BASES', 'PCT_INTRONIC_BASES', 
                    'PCT_RIBOSOMAL_BASES')
  contVar = 'Diagnosis'

  aadDiffExp <- performDifferentialExpressionAAD(cov, cnt, contVar, varOfInterest, gene.len, gene.gc)

>>>>

  # Formulate covariates matrix
  FactorCov = c('Diagnosis', 'Batch', 'Gender')
  ContCov = c('RIN', 'AAD', 'PMI',  'PCT_PF_READS_ALIGNED', 'PCT_CODING_BASES', 
              'PCT_INTERGENIC_BASES', 'PCT_INTRONIC_BASES', 'PCT_RIBOSOMAL_BASES')
  cov[,FactorCov] = lapply(cov[,FactorCov], as.factor)
  cov[,ContCov] = lapply(cov[,ContCov], as.numeric)
  rownames(cov) = cov$SampleID
  cov = cov[,c(FactorCov, ContCov)]
  cov$RIN2 = cov$RIN^2
  # assocStat = getAssociationStatistics(cov)

  # Perform differential expression between case-control
  if(any(unique(cov$BrainRegion) %in% c('DLPFC'))){
    varOfInterest = c('Diagnosis', 'Batch', 'Gender', 'RIN', 'AAD', 'PMI', 
                    'PCT_CODING_BASES', 'PCT_INTERGENIC_BASES')
  } else {
    if (any(unique(cov$BrainRegion) %in% c('FP', 'STG', 'PHG', 'IFG'))){
      varOfInterest = c('Diagnosis', 'Batch', 'Gender', 'RIN', 'AAD', 'PMI', 
                        'PCT_CODING_BASES', 'PCT_PF_READS_ALIGNED', 'PCT_INTERGENIC_BASES', 
                        'PCT_INTRONIC_BASES', 'RIN2')
    } else (any(unique(cov$BrainRegion) %in% c('CER', 'TCX'))) {
      varOfInterest = c('Diagnosis', 'Batch', 'Gender', 'RIN', 'AAD', 'PMI',
                        'PCT_INTERGENIC_BASES', 'PCT_INTRONIC_BASES', 
                        'PCT_RIBOSOMAL_BASES', 'PCT_CODING_BASES')
    }
  } 
  contVar = 'Diagnosis'

@@

  # Perform differential expression between case-control in a AAD specific manner
  aadDiffExp <- performDifferentialExpressionAAD(cov, cnt, contVar, varOfInterest, gene.len, gene.gc)

  # Perform differential expression between case-control in a gender specific manner
  cov$Diagnosis.Gender = factor(paste(cov$Diagnosis, cov$Gender, sep = '.'))
  if(any(unique(cov$BrainRegion) %in% c('DLPFC'))){
    varOfInterest = c('Diagnosis.Gender', 'Batch', 'Gender', 'RIN', 'AAD', 'PMI', 
                    'PCT_CODING_BASES', 'PCT_INTERGENIC_BASES')
  } else {
    if (any(unique(cov$BrainRegion) %in% c('FP', 'STG', 'PHG', 'IFG'))){
      varOfInterest = c('Diagnosis.Gender', 'Batch', 'Gender', 'RIN', 'AAD', 'PMI', 
                        'PCT_CODING_BASES', 'PCT_PF_READS_ALIGNED', 'PCT_INTERGENIC_BASES', 
                        'PCT_INTRONIC_BASES', 'RIN2')
    } else (any(unique(cov$BrainRegion) %in% c('CER', 'TCX'))) {
      varOfInterest = c('Diagnosis.Gender', 'Batch', 'Gender', 'RIN', 'AAD', 'PMI',
                        'PCT_INTERGENIC_BASES', 'PCT_INTRONIC_BASES', 
                        'PCT_RIBOSOMAL_BASES', 'PCT_CODING_BASES')
    }
  }
  contVar = 'Diagnosis.Gender'

@@
